mtcnn evaluation

### 2018-01-12 analysis-validation/mtcnn_evaluation.Rmd
random edits and new gold set candidates

500 frames were taken across all groups, half of them labeled as containing a face and half with no face.

@@

Join
```{r}
combined <- data %>%
  rename(detector_is_face = is_face) %>%
  inner_join(ground_truth_data, by = c("group", "video", "frame"))
```

>>>>

500 frames were taken across all groups, half of them labeled as containing a face and half with no face.
```{r}
library(tidyverse)
library(magrittr)
```

@@

For openpose only 
```{r}
data <- read_csv("data/final_output/openpose_results_truncated.csv") %>%
  distinct(name, frame, .keep_all = TRUE)
```

```{r}
contains_face <- function(n, l, r) {
  return(n != 0)
}
```

```{r}
data2 <- data %>%
  mutate(is_face = (LEye_conf != 0 | REye_conf != 0) | Nose_conf != 0) %>%
  select(group, name, frame, is_face) %>%
  rename(video = name)
```

Join
```{r}
combined <- data2 %>%
  rename(detector_is_face = is_face) %>%
  inner_join(ground_truth_data, by = c("group", "video", "frame"))
```
openpose, annoying
```{r}
combined %<>% 
  mutate(detector_is_face = ifelse(detector_is_face == TRUE, "True", "False"))
```
